---
title: "Final_Project_Code"
date: now
author: "Elliot Kunz, Andrea Pareja, Anson Wu, Caroline Ritchey"
format: 
  html:
    embed-resources: true
    code-tools: true
    toc: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

## PC 3

```{r setup}
library(tidyverse)
library(gt)
```

### Data Descriptions

In this analysis, we use data collected by Gallup World Poll on November 20, 2024 which contains the national average response to the question of life evaluations. We additionally include information from a dataset provided by Gapminder on the mean daily household per capita income. Our analysis includes the years 2005 - 2023.

### Hypothesis

We believe that as daily income increases, so does the happiness score (WHR). Typically higher incomes means more financial freedom, this lowers the stress that is built up from worrying about financial problems like cost of living. In the article, “Does more money correlate with greater happiness?” by Michele W. Berger, Matthew Killingsworth argues that “for most people larger incomes are associated with greater happiness” (Berger 2023).


```{r}
data1 <- read_csv("hapiscore_whr.csv", show_col_types = F)
data2 <- read_csv("mincpcap_cppp.csv", show_col_types = F)



clean_data1 <- data1 %>% 
  pivot_longer(cols = `2005`:`2023`,
              names_to = "year",
              values_to = "happiness")
  


clean_data2 <- data2 %>% 
  pivot_longer(cols = `1800`:`2100`,
              names_to = 'year',
              values_to = "daily_income")
  
  
data <- clean_data1 %>% 
  inner_join(clean_data2, 
             by = join_by(country == country, year == year)) %>% 
  na.omit()

kable(data, col.names = c("Country", "Year", "Happiness"," Daily Income"), align = "c", digits = 2)
```

### Works Cited

Berger, Michele W. “Does More Money Correlate with Greater Happiness?” Penn Today, University of Pennsylvania, 6 Mar. 2023, penntoday.upenn.edu/news/does-more-money-correlate-greater-happiness-Penn-Princeton-research.

Helliwell, John F., et al. \"World Happiness Report 2024.\" The World Happiness Report, 20 Mar. 2024, [worldhappiness.report/ed/2024/](http://worldhappiness.report/ed/2024/).

\"Poverty and Inequality Platform.\" Poverty and Inequality Platform, 2022, [pip.worldbank.org/#](http://pip.worldbank.org/#). 


## PC 4

```{r}
model <- glm(happiness ~ daily_income, data = data)
summary(model)

ggplot(data = data, mapping = aes(x = daily_income, y = happiness))+
  geom_point()+
  geom_smooth(colour = "blue")

```
